---
title: "5261_LDA"
author: "Jiahao Zhang"
date: "April 26, 2017"
output: pdf_document
---
## About LDA:
Linear discriminant analysis (LDA) is a generalization of Fisher's linear discriminant, a method used in statistics, pattern recognition and machine learning to find a linear combination of features that characterizes or separates two or more classes of objects or events. Assumptions of LDA are:
Gaussian Distribution. The standard implementation of the model assumes a Gaussian distribution of the input variables. Consider reviewing the univariate distributions of each attribute and using transforms to make them more Gaussian-looking (e.g. log and root for exponential distributions and Box-Cox for skewed distributions).

Same Variance. LDA assumes that each input variable has the same variance. It is almost always a good idea to standardize your data before using LDA so that it has a mean of 0 and a standard deviation of 1.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("/Users/ZHANGJIAHAO/Desktop/R-studio")
data<-read.csv("data.csv")
library(caret)
set.seed(1)
classer <-function(industry){
  Banks=data[data$GICS.Ind.Grp.Name==industry,]
  t=apply(Banks,2,function(x) sum(is.na(x)))/nrow(Banks)
  index=which(t>0.8) #delete the column with too many NAs
  Banks=Banks[,-index]
  
  
  
  Banks=data.frame(apply(Banks[,!colnames(Banks)%in%c("EQUITY","Date","GICS.Ind.Grp.Name")],2,function(x) {
    replace(x,is.na(x),mean(x,na.rm=TRUE))})) ## replace with mean
  Banks$RETURN<-ifelse(Banks$RETURN>0.1,"Good","Bad")
  Banks$RETURN <- as.factor(Banks$RETURN)
  cctrl1 <- trainControl(method = "cv", number = 3, returnResamp = "all",
                         classProbs = TRUE, 
                         summaryFunction = twoClassSummary)
  
  index <- sample(1:nrow(Banks),round(0.9*nrow(Banks)))
  train.cv <- Banks[index,]
  test.cv <- Banks[-index,]
  test_class_cv_form <- train(RETURN ~ ., data = train.cv, 
                              method = "lda", 
                              trControl = cctrl1,
                              metric = "ROC", 
                              preProc = c("center", "scale"))
  test_class_pred_form <- predict(test_class_cv_form, test.cv[, -ncol(test.cv)])
  error <- mean(test_class_pred_form==test.cv$RETURN)
  return(list(error))
  
}
list.in <- list("Real Estate","Health Care Equipment & Services","Software & Services","Pharmaceuticals, Biotechnology & Life Sciences",
                "Capital Goods",
                "Banks")
names(list.in)<-c("Real Estate","Health Care Equipment & Services","Software & Services","Pharmaceuticals, Biotechnology & Life Sciences",
                  "Capital Goods",
                  "Banks")
result <- unlist(lapply(list.in,classer))
accuracy <- data.frame(result)
accuracy



```